\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-23 manuscript/manuscript.tex
comments

First, let us consider how the KS statistic is typically computed for a sample
with no dependence structure.
Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
distribution fitted onto $X_t$, and let 
$F_n$ denote the empirical distribution function based on $X_1,...,X_n$
\jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
  not been defined.}
\mc{addressed}

Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}

@@

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
$b \in \{1, \ldots, B\}$.  
Block-bootstrap can be done with overlapping or moving blocks.
Define 
moving blocks (assuming $l > 1$) as:
\begin{equation*}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation*}
A common 
function for block size that is considered optimal is 
$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
which was adopted in this study.

We then use the bootstrap distribution to construct an approximation of
the KS statistic.
\jy{Not good opening sentence}\mc{addressed}
In this case, we can 
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
\jy{The second term: does it depend on $b$? }\mc{addressed}
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$,
and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ to
approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.

We can compute $E[F^{(b)}_n(x)]$ and
\jy{Are these two terms $b$-specific?}\mc{addressed}
$E[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
depending on the types of block bootstrap we use). One can compute 
$F^{(b)}_n$ 
and $\hat\theta^{(b)}_n$ based on
the $b$th bootstrap sample. Then
$E[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
$E[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
In this case, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$.

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows.
\begin{enumerate}
\item
  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical distribution 
  $F_n$
  with replacement.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}

@@

\jy{How many replicates were used to estimate the size and power?}
\mc{addressed}

@@

@@

@@

>>>>

First, let us consider how the KS statistic is typically computed for a sample
with no dependence structure.
Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
distribution fitted onto $X_t$, and let 
$F_n$ denote the empirical distribution function based on $X_1,...,X_n$
Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}

@@

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
$b \in \{1, \ldots, B\}$.  
Block-bootstrap can be done with overlapping or moving blocks.
Define 
moving blocks (assuming $l > 1$) as:
\begin{equation*}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation*}
A common 
function for block size that is considered optimal is 
$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
which was adopted in this study.

We then use bootstrap to approximate the distribuition of
the KS statistic under $H_0$. In this case, we can 
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$,
and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ to
approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.

We can compute $E[F^{(b)}_n(x)]$ and
$E[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
depending on the types of block bootstrap we use). One can compute 
$F^{(b)}_n$ 
and $\hat\theta^{(b)}_n$ based on
the $b$th bootstrap sample. Then
$E[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
$E[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
In this case, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
$b =1, \ldots, B$, is considered a draw from a distribution that approximates
the distribution of $T_n$. Therefore, the p-value of the observed statistic
$T_n$ can be assessed by positioning it agains the empirical distribution of
$T_n^{(b)}$, $b = 1, \ldots, B$.

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows.
\jy{Whrere is the 'block' part?}
\begin{enumerate}
\item
  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical
  distribution~$F_n$.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}

@@

@@

\jy{The large number decimals in the old table: some numerical issues?}

@@

\jy{Consider presenting this in a graph. Try explaining the pattern.
  Keep the notations consistent: $n$ and n are different.}

@@

\jy{I'm surprised that t does not fit well even for two years data.}

\jy{Report the autocorrelation estimate of residual and residual squared in the
  text.}
